---
title: "Assignment 02"
author: "Md Nakir Ahmed"
format: html
editor: visual
---

## 1) Lab 01 and Lab 02

Please check the lab section to see **Lab 01** and **Lab 02**.

------------------------------------------------------------------------

## 2) Load and Explore the TEDS2016 Dataset

```{r}
library(haven)
library(dplyr)
library(ggplot2)
library(car)

TEDS_2016 <- read_stata("https://github.com/datageneration/home/blob/master/DataProgramming/data/TEDS_2016.dta?raw=true")
head(TEDS_2016)
str(TEDS_2016)
summary(TEDS_2016)
```

------------------------------------------------------------------------

## 3) Identify Problems with the Dataset

We identified missing values in the dataset using `colSums(is.na(...))`. This tells us how many values are missing per column, which is important before running any models or summaries.

```{r}
colSums(is.na(TEDS_2016))
```

------------------------------------------------------------------------

## 4) Handle Missing Values

We used `na.omit()` to remove rows with missing values. This ensures we’re working with complete cases and helps prevent errors in analysis. After removal, we confirmed no missing values remain.

```{r}
TEDS_2016_cleaned <- na.omit(TEDS_2016)
colSums(is.na(TEDS_2016_cleaned))
```

------------------------------------------------------------------------

## 5) Explore Relationship Between Tondu and Other Variables

We ran a linear regression to examine how **Tondu** is affected by predictors like **gender**, **party support (DPP)**, **age**, **income**, **education**, **ethnic identity**, and **economic perception**.

The regression model helps quantify which variables have significant effects on Tondu.

```{r}
TEDS_2016_cleaned$female <- as.factor(TEDS_2016_cleaned$female)
TEDS_2016_cleaned$DPP <- as.factor(TEDS_2016_cleaned$DPP)
TEDS_2016_cleaned$Taiwanese <- as.factor(TEDS_2016_cleaned$Taiwanese)
TEDS_2016_cleaned$Econ_worse <- as.factor(TEDS_2016_cleaned$Econ_worse)

model <- lm(Tondu ~ female + DPP + age + income + edu + Taiwanese + Econ_worse, data = TEDS_2016_cleaned)
summary(model)
```

### Visualization of Relationships

We used boxplots to explore how the variable **Tondu** (support for unification or independence) varies by categorical variables such as **gender** and **DPP affiliation**.

-   The first plot shows differences in Tondu scores between male and female respondents.
-   The second plot compares Tondu scores for people who do or do not support the DPP.

```{r}
ggplot(TEDS_2016_cleaned, aes(x = female, y = Tondu, fill = female)) +
  geom_boxplot() +
  labs(title = "Tondu by Gender", x = "Female", y = "Tondu") +
  theme_minimal()

ggplot(TEDS_2016_cleaned, aes(x = DPP, y = Tondu, fill = DPP)) +
  geom_boxplot() +
  labs(title = "Tondu by DPP Affiliation", x = "DPP", y = "Tondu") +
  theme_minimal()
```

------------------------------------------------------------------------

## 6) Explore the votetsai Variable

The variable `votetsai` shows whether a respondent voted for Tsai Ing-wen. A bar chart helps us understand how common support for Tsai is among the respondents.

```{r}
ggplot(na.omit(TEDS_2016_cleaned), aes(x = factor(votetsai))) +
  geom_bar(fill = "steelblue") +
  labs(title = "Distribution of votetsai", x = "Vote for Tsai Ing-wen", y = "Count") +
  theme_minimal()

```

------------------------------------------------------------------------

## 7) Frequency Table and Bar Chart for Tondu

To better understand the distribution of political preferences in Taiwan, we recoded the numeric **Tondu** variable into labeled categories such as: - "Unification now", "Independence now", "Status quo forever", etc.

Then we used a bar chart to display the frequency of each preference. This helps visually compare how common each political stance is in the dataset.

```{r}
TEDS_2016$Tondu <- factor(TEDS_2016$Tondu,
                          labels = c("Unification now",
                                     "Status quo, unif. in future",
                                     "Status quo, decide later",
                                     "Status quo forever",
                                     "Status quo, indep. in future",
                                     "Independence now",
                                     "No response"))

table(TEDS_2016$Tondu)

ggplot(data.frame(Tondu = TEDS_2016$Tondu), aes(x = Tondu)) +
  geom_bar(fill = "coral") +
  theme_minimal() +
  labs(title = "Bar Chart of Tondu Responses", x = "Tondu", y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
